---
title: "Curriculum Vitae"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
 html_document:
  toc: true
  toc_float: true
  theme: "journal"
 # pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
table <- 
 function (col1, col2, url, doi) {
  if (missing(url) && missing(doi)) {
   url <- ""
  } else if (!missing(doi)) {
    url <- paste("http://dx.doi.org/", doi, sep = "")
  }
  url <- ifelse(url == "", "", paste('[<a class="texto" href="', url, '">link</a>]'))
  paste('<table><tbody><tr valign="top"><td width="148px">', col1, 
     '</td><td width="624px">', col2, url, '</td></tr></tbody></table>', sep = " ")
 }
```

## Personal Information

### Identification and Contact

`r table("Name", "<b>Alessandro Samuel Rosa</b>")`

`r table("Citation", "SAMUEL-ROSA, Alessandro; ROSA, Alessandro Samuel; ROSA, Alessandro Samuel da")`

`r table("Nationality", "Brazilian")`

`r table("Date and place of birth", "05 June 1985, Tapera, Rio Grande do Sul")`

`r table("Address", "
Rua Walcreuze Guimarães, 545<br>
Bairro Boa Esperança<br>
CEP 23894458<br>
Seropédica, Rio de Janeiro, Brazil")`

`r table("Telephone", "+55 (21) 2682-8516 or +55 (21) 97319-3838")`

`r table("E-mail", "alessandrosamuelrosa at gmail.com")`

`r table("Skype", "alessandrosamuel")`

`r table("Webpage", "https://www.researchgate.net/profile/Alessandro_Samuel-Rosa")`

`r table("Complete CV", "http://lattes.cnpq.br/1609751519717461")`

### Qualifications

`r table("", 
"Alessandro Samuel-Rosa has studied soil science and works at the Federal University of Santa Maria (UFSM) 
since the end of 2016. After his early work on the interactions between land use and soil quality
at UFSM, in 2012 he moved to the field of Pedometrics. Collaboration with researchers from the National 
Centre for Research on Soils (Embrapa Soils), International Soil Reference and Information Centre (ISRIC),
Wageningen University and Research Centre (WUR) and Federal Rural University of Rio de Janeiro (UFRRJ) 
enabled him to master multiple pedometric methods and techniques. His main research interest is on soil 
spatial modelling with a focus on sampling strategies, model selection and calibration, and uncertainty
analysis. He has recently published some relevant papers in peer-reviewed, international journals on these 
topics. He is the author of two R-packages, namely, pedometrics -- a collection of functions for spatial
exploratory data analysis and model calibration -- and spsann -- an implementation of simulated annealing to
optimize spatial sample configurations. Both packages are widely used, each with more than 200 downloads per
month on average from the RStudio CRAN mirror.")`

`r table("Gustavo Vasques", 
"I have had the pleasure of co-advising Alessandro Samuel Rosa during his doctoral studies [...]. In this 
period I came to know Alessandro’s professional and personal skills and am confident to say that he is an
outstanding researcher and person. He is really smart, organized, and meticulous with everything he does. [...]
I must add that doing research and publishing with Alessandro is easy, as he leads and guides us through the
whole process very smoothly, be it research (data collection, analysis, interpretation, etc.) or publication 
(write-up, submission, review, etc.). This is partly due to his excellent English and writing skills.")`

`r table("Gerard Heuvelink",
"Alessandro came to Wageningen to work on his PhD-research for twelve months in 2014 and also came for a 
shorter period in 2015. During these periods I had ample time to get to know him better. Without any doubt I 
can say that he is among the best PhD students that I have supervised. He is intelligent, dedicated, 
meticulous, cooperative, hard-working and self-critical. He can master new methods and techniques very quickly.
He is strong in soil science, statistics as well as in information science. Above all, he is creative and
innovative. His level of English and scientific writing skills are excellent too. [...] Not only is he very
productive, in addition the scientific level of his work is very high.")`

### Education and Degrees

`r table('2012--2016', 'PhD in Agronomy -- Soil Science.<br>
Federal Rural University of Rio de Janeiro, UFRRJ, Brazil, with collaborative period in the International
Soil Reference and Information Centre (ISRIC) (Advisor: 
<a href="http://www.isric.org/users/gerard-heuvelink">Gerard Heuvelink</a>).<br>
Title: Analysis of Sources of Uncertainty in Soil Spatial Modelling<br>
Advisor: <a href="http://lattes.cnpq.br/7882538227876962">Lúcia Anjos</a>.<br>
Co-advisor: <a href="http://lattes.cnpq.br/1838153897546051">Gustavo Vasques</a>.<br>
Grantee of the National Council for Scientific and Technological Development (CNPq), Brazil.')`

`r table('2010--2012', 'MSc in Soil Science.<br>
Federal University of Santa Maria, UFSM, Brazil.<br>
Title: Soil Properties Spatial Prediction Functions<br>
Advisor: <a href="http://lattes.cnpq.br/3735884911693854">Ricardo Dalmolin</a>.<br>
Grantee of the National Council for Scientific and Technological Development (CNPq), Brazil.')`

`r table('2004--2010', 'BSc in Agronomy.<br>
Federal University of Santa Maria (UFSM), Brazil.<br>
Advisor: <a href="http://lattes.cnpq.br/3735884911693854">Ricardo Dalmolin</a>.<br>')`

### Postdoctorate

`r table("Dec 2016--", "Federal University of Santa Maria, UFSM, Brazil.<br>
Grantee of the Coordination for the Improvement of Higher Education Personnel (CAPES), Brazil.<br>
Major Area: Agrarian Sciences. Area: Soil Science. Sub-area: Pedometrics.")`

`r table("Mar--Nov 2016", "Federal Rural University of Rio de Janeiro, UFRRJ, Brazil.<br>
Grantee of the Coordination for the Improvement of Higher Education Personnel (CAPES), Brazil.<br>
Major Area: Agrarian Sciences. Area: Soil Science. Sub-area: Pedometrics.")`

### Specific Knowledge

`r table("Former languages", "English (good), Spanish (fair)")`

`r table("Computer languages", "R (good), (La)TeX (good), C++ (slight)")`

### Awards

`r table("2014", "geoENV 2014 best student oral presentation and poster (3rd place)")`

## Selected Activities

### Training and Lecturing

`r table("10 Oct 2016", "One-day course 'Introduction to spatial sampling using R' at Federal
Rural University of Rio de Janeiro (Postgraduate Course in Agronomy--Soil Science)")`

`r table("Feb--Mar 2016", "Five-day course 'Special Topics in Soil Science -- Using Big Data in Soil
Science' (in cooperation with Eloi Ribeiro) at São Paulo State University (Postgraduate Course in Soil
Science)")`

### Conference Organization

`r table(2017, "Member of the scientific committee of the Pedometrics conference in Wageningen, the
Netherlands")`

`r table(2016, "Member of the organizing committee of the first Brazilian Meeting on Pedometrics in Campinas,
São Paulo")`

### Refereeing

`r table("2012--present", "Alessandro Samuel-Rosa has refereed papers for the following journals: 
Ciência Rural, Spatial Statistics, Floresta & Ambiente, Earth System Science Data.")`

### Professional association

`r table("2015--present", "Member of the Pedometrics Commission of the Brazilian Society of Soil Science")`

`r table("2014--2015", "Member of the European Geosciences Union")`

`r table("2012--present", "Member of the Brazilian Society of Soil Science and the International Union of
Soil Sciences")`

## Selected Publications

### Journal Articles 

`r table(2017, "VILLELA, A. L. O.; <b>SAMUEL-ROSA, Alessandro</b>; VASQUES, G. M.; CEDDIA, M. B. Digital soil
mapping in the poorly-accessible Brazilian Amazon using a reference area. (IN PREPARATION)",
"https://www.researchgate.net/project/Digital-soil-mapping-in-the-Brazilian-Amazon--using-the-knowledge-from-a-reference-area")`

`r table(2017, "ALHO, C. F. B. V.; <b>SAMUEL-ROSA, Alessandro</b>; HIEMSTRA, T.; KUYPER, T. W.; 
MARTINS, G. C.; TEIXEIRA, W. G. Spatial modelling of total carbon, calcium and phosphorus stocks in Amazonian 
Dark Earths. (IN PREPARATION)",
"https://www.researchgate.net/project/Spatial-modelling-of-elemental-stocks-in-Amazonian-Dark-Earths")`

`r table(2017, "<b>SAMUEL-ROSA, Alessandro</b>; BRUS, D. J.; HEUVELINK, G. B.; VASQUES, G. M.; ANJOS, L. H. C.
Optimization of sample configurations for spatial trend estimation for soil mapping. (IN PREPARATION)",
"https://www.researchgate.net/project/Optimization-of-sample-configurations-for-spatial-trend-estimation-for-soil-mapping")`

`r table(2016, "COSTA, E. M.; <b>SAMUEL-ROSA, Alessandro</b>; ANJOS, L. H. C. Choosing a digital
elevation model for digital soil mapping. Annals of the Brazilian Academy of Sciences. (SUBMMITED)",
"https://www.researchgate.net/project/Choosing-a-digital-elevation-model-for-digital-soil-mapping")`

`r table(2015, "<b>SAMUEL-ROSA, Alessandro</b>; HEUVELINK, G. B.; VASQUES, G. M.; ANJOS, L. H. 
C. Do more detailed environmental covariates deliver more accurate soil maps? Geoderma, v. 243-244, 
p. 214-227.", doi = "10.1016/j.geoderma.2014.12.017")`

`r table(2014, "HENGL, T.; JESUS, J. M.; MACMILLAN, R. A.; BATJES, N. H.; HEUVELINK, G. B.; RIBEIRO, E. C.;
<b>SAMUEL-ROSA, Alessandro</b>; KEMPEN, B.; LEENAARS, J. G.; WALSH, M. G.; GONZALEZ, M. R. 
SoilGrids1km---Global Soil Information Based on Automated Mapping. Plos One, v. 9, p. e105992.",
doi = "10.1371/journal.pone.0105992")`

`r table(2013, "<b>SAMUEL-ROSA, Alessandro</b>; DALMOLIN, R. S. D.; MIGUEL, P. Building predictive models of 
soil particle-size distribution. Brazilian Journal of Soil Science, v. 37, p. 422-430.",
doi = "10.1590/s0100-06832013000200013")`

`r table(2013, "<b>SAMUEL-ROSA, Alessandro</b>; DALMOLIN, R. S. D.; MIGUEL, P.; ZALAMENA, J.; DICK, D. P. 
The effect of intrinsic soil properties on soil quality assessments. Brazilian Journal of Soil Science, 
v. 37, p. 1236-1244.", doi = "10.1590/s0100-06832013000500013")`

`r table(2012, "PEDRON, F. A.; <b>SAMUEL-ROSA, Alessandro</b>; DALMOLIN, R. S. D. Variation in pedological
characteristics and the taxonomic classification of Argissolos (Ultisols and Alfisols) derived from 
sedimentary rocks. Brazilian Journal of Soil Science, v. 36, p. 1-9.", 
doi = "10.1590/S0100-06832012000100001")`

`r table(2011, "<b>SAMUEL-ROSA, Alessandro</b>; DALMOLIN, R. S. D.; PEDRON, F. A. Characterization of soil 
covers in closed landfill sites with (geo)statistical tools. Engenharia Sanitária e Ambiental, v. 16, p. 
121-126.", "http://www.scielo.br/scielo.php?script=sci_arttext&pid=S1413-41522011000200004&lng=en&tlng=pt")`

### Proceedings Papers

`r table(2013, "<b>SAMUEL-ROSA, Alessandro</b>; ANJOS, L. H. C.; VASQUES, G. M.; ANTUNES, M. A. H.; DALMOLIN, 
R. S. D. Identifying and correcting oblique striping in the Topodata digital elevation model. In: Proceedings 
of the XXXIV Brazilian Congress of Soil Science, Florianópolis, Brazil. p. 1-4.",
"https://www.researchgate.net/publication/262487636_Identifying_and_correcting_oblique_striping_in_the_Topodata_digital_elevation_model")`

`r table(2012, "<b>SAMUEL-ROSA, Alessandro</b>; DALMOLIN, R. S. D.; MIGUEL, P. Larger geologic complexity
implies larger uncertainty. In: Proceedings of the Tenth International Symposium on Spatial Accuracy 
Assessment in Natural Resources and Environment Sciences, Florianópolis, Brazil. p. 227-232.",
"http://www.spatial-accuracy.org/Accuracy2012")`

`r table(2010, "DALMOLIN, R. S. D.; DICK, D. P.; KLAMT, E.; COUTO, E. G.; <b>SAMUEL-ROSA, Alessandro</b>.
Mineralogical assemblage and iron oxides of soils of the Pantanal biome, Brazil. In: Proceedings of the 19th
World Congress of Soil Science, Brisbane, Australia. p. 52-55.")`

### Abstracts in Proceedings

`r table(2015, "<b>SAMUEL-ROSA, Alessandro</b>; HEUVELINK, G. B. M.; VASQUES, G. M.; ANJOS, L. H. C. spsann --
optimization of sample patterns using spatial simulated annealing. In: Proceedings of the European Geosciences
Union General Assembly 2015, Wien, Austria. p. EGU2015-7780.",
"http://meetingorganizer.copernicus.org/EGU2015/EGU2015-7780.pdf")`

`r table(2015, "<b>SAMUEL-ROSA, Alessandro</b>; BRUS, D. J.; VASQUES, G. M.; ANJOS, L. H. C. Optimization of
sample configurations for spatial trend estimation. In: Proceedings of the Pedometrics 2015, Córdoba, Spain.",
doi = "10.13140/RG.2.1.2198.5769")`

`r table(2015, "<b>SAMUEL-ROSA, Alessandro</b>; HEUVELINK, G. B.; VASQUES, G. M.; ANJOS, L. H. C. Optimization
of sample configurations for variogram estimation. In: Proceedings of Pedometrics 2015, Córdoba, Spain.",
doi = "10.13140/RG.2.1.1412.1440")`

`r table(2014, "<b>SAMUEL-ROSA, Alessandro</b>; ANJOS, L. H. C.; VASQUES, G. M.. An approach to help 
formalizing the purposive sampling strategy of classical soil surveys. In: Proceedings of the 20th World 
Congress of Soil Science, Jeju, South Korea.", doi = "10.13140/RG.2.1.2380.0563")`

`r table(2014, "ANJOS, L. H. C.; <b>SAMUEL-ROSA, Alessandro</b>; SCHAD, P. New qualifier in WRB based on
Brazilian soils with high iron contents. In: Proceedings of the 20th World Congress of Soil Science, Jeju, 
South Korea.", doi = "10.13140/2.1.3720.8647")`

`r table(2014, "<b>SAMUEL-ROSA, Alessandro</b>; HEUVELINK, G. B. M.; VASQUES, G. M.; ANJOS, L. H. C. Spatial
point pattern analysis of soil survey sampling locations. In: Proceedings of the 10th Conference on
Geostatistics for Environmental Applications, Paris, France.", doi = "10.13140/RG.2.1.3428.6329")`

### Computer Programs

`r table(2016, "<b>SAMUEL-ROSA, Alessandro</b>. spsann: Optimization of Sample Configurations using Spatial 
Simulated Annealing. R package version 2.0-0.", "https://CRAN.R-project.org/package=spsann")`

`r table(2015, "<b>SAMUEL-ROSA, Alessandro</b>. pedometrics: Pedometric Tools and Techniques. R package 
version 0.6-6.9000.", "https://CRAN.R-project.org/package=pedometrics")`
